---
title: "Analyse résultats"
author: "Thomas Guyet and Michael Mbouopda"
date: "21/02/2022"
output: pdf_document
---

```{r clean up, include=FALSE}
rm(list=ls())
rep_results="./"
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(scmamp)
```


# Comparison of Local models
In this section, we use only the data of local models

```{r data load, message=FALSE, echo=FALSE, include=FALSE}

# old results from Thomas
files= c( paste0(rep_results,'oldTG_local_part1.csv'), 
          paste0(rep_results,'oldTG_local_part2.csv'),
          paste0(rep_results,'oldTG_local_part3.csv'),
          paste0(rep_results,'oldTG_local_part4.csv'),
          paste0(rep_results,'oldTG_local_cmpl.csv'),
          paste0(rep_results,'oldTG_local_xgb.csv') )
data <- files %>% map_df( ~ read_tsv(.) )
data['rmse'] <- sqrt(data['mse'])
data <- data %>% filter( approx_exo==FALSE ) %>% select(-c('r','mse','type','use_exo_bdlisa', 'approx_exo'))%>%rename(model = id_method_ML)

# Add Deep AR results
data_deepar = read_csv("local_DeepAR.csv", col_select=c('item_id','model','rmse','rmsse','use_exo_evo', 'use_exo_rain'))%>%rename( id_piezo=item_id, use_exo_eto=use_exo_evo )
data <- bind_rows(data,data_deepar)

data_deepar = read_csv("global_DeepAR.csv", col_select=c('item_id','model','rmse','rmsse','use_exo_evo', 'use_exo_rain'))%>%rename( id_piezo=item_id, use_exo_eto=use_exo_evo )
data <- bind_rows(data,data_deepar)

# Add Prophet results
# files= c( paste0(rep_results,'local_prophet.csv'), 
#           paste0(rep_results,'local_neuralprophet.csv'),
#           paste0(rep_results,'local_Conv.csv'))
# 
# newdata <- files %>% map_df( ~ read_csv(.) ) %>% select(c('bss_code','model','rmse_test','rmsse_test','use_exo_evo', 'use_exo_rain'))%>%rename( rmse=rmse_test, rmsse=rmsse_test, id_piezo=bss_code, use_exo_eto=use_exo_evo )
# data <- bind_rows(data,newdata)
# 
# rm(data_prophet,newdata)
data
```

## Comparison of RMSSE without exogenous variables
In this section we compare the different forecasting methods while not using exogenous data ...
We use RMSSE measurements. 


```{r "cmp sans données exogènes", echo=FALSE, message=FALSE, prompt=FALSE, warning=FALSE, fig.path="figures/"}
ggdata  = data %>% filter( use_exo_rain==FALSE &  
                             use_exo_eto==FALSE) %>% 
  select( id_piezo, model, rmsse, rmse)

ggplot( ggdata) +
  geom_boxplot( aes(x=model, y=rmse) ) +
  theme_bw()+
  ylim(0,10) +
  labs(x = "Regresseur", y = "RMSE") +
  theme(legend.position = c(0.1, 0.85), axis.title.x = element_blank())

ggplot( ggdata) +
  geom_boxplot( aes(x=model, y=rmsse) ) +
  theme_bw()+
  ylim(0,50) +
  labs(x = "Regresseur", y = "RMSSE") +
  theme(legend.position = c(0.1, 0.85), axis.title.x = element_blank())
#ggsave("expe_cmp_ml.pdf", width = 7, height = 4)
```

We can notice that the DeepAR approach outperforms the other approaches based on various auto-regressive functions and Prophet.

We now compute the Critical Difference Diagram using the same comparison setting. The Figure below confirms the results: DeepAR significantly outperforms the other approaches.

```{r, message=FALSE, echo=FALSE, prompt=FALSE, warning=FALSE, fig.path="figures/", fig.width=15}

# Critical differences diagram
df = ggdata %>% select(id_piezo, model, rmsse)%>%group_by(id_piezo, model)%>%
  summarise( rmsse=mean(rmsse))%>%spread(model, rmsse)%>%ungroup()%>%drop_na()

cmpmat<-df%>%select(-id_piezo)

#pdf(file = "cd_cmp_ml.pdf", width = 7, height = 4)
#plotCD(-cmpmat, cex = 1)
#dev.off()
plotCD(-cmpmat, cex = 1)
```



# Comparaison Local/Global for DeepAR
```{r, message=FALSE, echo=FALSE, include=FALSE}
data_deepar = read_csv("local_DeepAR.csv", col_select=c('item_id','model','rmse','rmsse','use_exo_evo', 'use_exo_rain'))%>%rename( id_piezo=item_id, use_exo_eto=use_exo_evo )
data_deepar['type']="local"
data <- data_deepar

data_deepar = read_csv("global_DeepAR.csv", col_select=c('item_id','model','rmse','rmsse','use_exo_evo', 'use_exo_rain'))%>%rename( id_piezo=item_id, use_exo_eto=use_exo_evo )
data_deepar['type']="global"
data <- bind_rows(data,data_deepar)
```

```{r "cmp local/global", echo=FALSE, message=FALSE, prompt=FALSE, warning=FALSE, fig.path="figures/"}
ggdata  = data %>% filter( use_exo_rain==FALSE &
                             use_exo_eto==FALSE) %>% 
  select( id_piezo, type, rmsse, rmse)

ggplot( ggdata) +
  geom_violin( aes(x=type, y=rmsse) ) +
  theme_bw()+
  ylim(c(0,50)) +
  labs(x = "Regresseur", y = "RMSSE") +
  ylim(0,10) +
  theme(legend.position = c(0.1, 0.85), axis.title.x = element_blank())


ggplot( ggdata) +
  geom_boxplot( aes(x=type, y=rmsse) ) +
  theme_bw()+
  ylim(c(0,50)) +
  labs(x = "Regresseur", y = "RMSSE") +
  ylim(0,10) +
  theme(legend.position = c(0.1, 0.85), axis.title.x = element_blank())
```

```{r, message=FALSE, echo=FALSE, prompt=FALSE, warning=FALSE, fig.path="figures/"}

# Critical differences diagram
df = ggdata %>% select(id_piezo, type, rmsse)%>%group_by(id_piezo, type)%>%
  summarise( rmsse=mean(rmsse))%>%spread(type, rmsse)%>%ungroup()%>%drop_na()

cmpmat<-df%>%select(-id_piezo)
plotCD(-cmpmat, cex = 1)
```

## Does the global model generalize well with respect to the piezometers?

In this section, the question is whether the global model trained on a set of piezometers can be used to make accurate forecasting (for the same period) for piezometers out of the training set.

We trained the model on 70\% of the piezometers and evaluate the forecast on the remaining 30\%.  
We repeated 4 times this experiment (4-folds).

```{r, message=FALSE, echo=FALSE, include=FALSE}
data_deepar_cv = read_csv("DeepAREstimator_global_cv.csv", col_select=c('item_id','model','rmse','rmsse','use_exo_evo', 'use_exo_rain','fold'))%>%rename( id_piezo=item_id, use_exo_eto=use_exo_evo )
data_deepar_cv['type']="global_cv"
```

```{r "cmp local/global", echo=FALSE, message=FALSE, prompt=FALSE, warning=FALSE, fig.path="figures/"}
ggdata  = data_deepar_cv %>% filter( use_exo_rain==FALSE &
                             use_exo_eto==FALSE) %>% 
  select( id_piezo, fold, rmsse, rmse)
ggdata$fold = as.factor(ggdata$fold)

ggplot( ggdata) +
  geom_violin( aes(x=fold, y=rmsse) ) +
  theme_bw()+
  ylim(c(0,50)) +
  labs(x = "Estimator", y = "RMSSE") +
  #ylim(0,10) +
  theme(legend.position = c(0.1, 0.85), axis.title.x = element_blank())
```
